### 2018-07-02 pilot_manuscript.Rmd
Wrote more and (very basically) outlined some other sections

```{r load_packages, include = FALSE}
library("papaja")
```

# Method

@@

Once data collection ended, the text was scanned using the ngram package in *R*. This was done in order to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.
```{r data-cleanup, eval=FALSE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

#let's look at the means
tapply(final$hperhi, final$Source, mean)
tapply(final$hperlo, final$Source, mean)
tapply(final$fperhi, final$Source, mean)
tapply(final$fperlo, final$Source, mean)
tapply(final$iperhi, final$Source, mean)
tapply(final$iperlo, final$Source, mean)
tapply(final$aperhi, final$Source, mean)
tapply(final$aperlo, final$Source, mean)
tapply(final$pperhi, final$Source, mean)
tapply(final$pperlo, final$Source, mean)
```
Usung the "nlme" library in *R*, a 2 X 5 multillevel model with news source as a random intercept was run. *IMMA NEED SOME HELP WITH HOW TO STRUCTURE THIS PART :)*
```{r mlm, eval=FALSE, include=FALSE}
##Attempt at MLM
mlm_data = final[ , -c(3:28) ]
library(reshape)
long_mlm = melt(mlm_data,
                id = c("X", "Source"))
colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
long_mlm$lean = factor(long_mlm$Source,
                       levels = names(table(long_mlm$Source)),
                       labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
long_mlm$lean = gsub("1", "", long_mlm$lean)

@@

# Results

# Discussion

>>>>

```{r load_packages, include = FALSE}
library("papaja")
```
# Introduction
Talk about MFT, MFQ, MFD
Talk about political discourse, nature of news media in 2018/Trump era
This project brings the two together in holy matrimony.
# Method

@@

Once data collection ended, the text was scanned using the "ngram" package in *R*. This was done in order to remove articles that came through as blank text, as well as to eliminate text picked up from the Disqus commenting system used by certain websites. At this point, duplicate articles were discarded.
```{r data-cleanup, eval=FALSE, include=FALSE}
##pull in the data
master = read.csv("overalldata.csv", stringsAsFactors = F)

@@

#let's look at the means
tapply(final$hperhi, final$Source, mean)
tapply(final$hperlo, final$Source, mean)
tapply(final$fperhi, final$Source, mean)
tapply(final$fperlo, final$Source, mean)
tapply(final$iperhi, final$Source, mean)
tapply(final$iperlo, final$Source, mean)
tapply(final$aperhi, final$Source, mean)
tapply(final$aperlo, final$Source, mean)
tapply(final$pperhi, final$Source, mean)
tapply(final$pperlo, final$Source, mean)
```
Usung the "nlme" library in *R*, a 2 X 5 multillevel model with news source as a random intercept was run. First, an intercept-only model was run, followed by a random intercept model. Next, a predictor model with political lean predicting percent of MFD words, a model adding MFD category (i.e. "harm-positive," "harm-negative", etc.) as a predictor, and a model with the interaction of political lean and MFD category predicting percent were run. Finally, a series of 10 models were run with political lean predicting percent split into the 10 MFD categories.
```{r mlm, eval=FALSE, include=FALSE}
##Attempt at MLM
mlm_data = final[ , -c(3:28) ]
library(reshape)
long_mlm = melt(mlm_data,
                id = c("X", "Source"))
colnames(long_mlm) = c("partno", "Source", "moraltype", "percent")
long_mlm$lean = factor(long_mlm$Source,
                       levels = names(table(long_mlm$Source)),
                       labels = c("Conservative1", "Conservative",
                                  "Liberal1", "Liberal"))
long_mlm$lean = gsub("1", "", long_mlm$lean)

@@

# Results
NUMBERS!!!
# Discussion
How it turned out
What to do for future project
Argue: why is still a good thing to study??
